Observed vs. Simulated Year Comparison

### 2023-04-18 03-post-process/compare-sim-to-obs.Rmd
Aesthetic updates to sim-vs-obs

```{r ratio_plot fn}
ratio_plot = function(ratios, line_y, pt_fn = mean, ...) {

@@

  # set graphics parameters
  par(mar = c(7,1,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")

  # make an empty plot with the right dimensions
  mp = barplot(summs["50%",], col = "white", ylab = "", border = "white", las = 2,
               ylim = c(min(0, min(summs, na.rm = TRUE)), max(summs, na.rm = TRUE)) * 1.1, ...)

@@

  # create an "acceptable region"
  usr = par("usr"); rect(usr[1], line_y - 0.25, usr[2], line_y + 0.25, col = "grey90", border = NA)
  abline(h = line_y, lty = 2, col = "grey")

@@

```{r ratio_plots fn}
ratio_plots = function(x, main) {
  par(mfrow = c(1,3), oma = c(0,2,2,0))
  ratio_plot(x[,"sim-v-obs","cv",], main = "CV", pt_fn = geomean, line_y = 1)
  ratio_plot(x[,"sim-v-obs","mean",], main = "Mean", pt_fn = geomean, line_y = 1)
  ratio_plot(x[,"sim-v-obs","acf",], main = "ACF (Sim - Obs)", pt_fn = mean, line_y = 0)
  mtext(side = 2, outer = TRUE, adj = 0.75, line = 1, "Ratio (Sim:Obs)")
  mtext(side = 3, outer = TRUE, line = 0.5, main, cex = 1.25, font = 2)
}
```

```{r vals_plot fn}
vals_plot = function(vals, ...) {
  f = function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975), na.rm = TRUE)

@@

  par(mar = c(7,1,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")
  mp = barplot(summs[,"50%",], beside = TRUE, col = "white", border = "white", ylim = range(summs, na.rm = TRUE) + diff(range(summs, na.rm = TRUE)) * c(-0.05,0.05), xaxt = "n", ...)
  segments(mp, summs[,"2.5%",], mp, summs[,"97.5%",], col = c("red", "blue"))
  segments(mp, summs[,"25%",], mp, summs[,"75%",], col = c("red", "blue"), lwd = 6)
  points(y = summs[,"50%",], x = mp, col = c("red", "blue"), pch = 3, cex = 1.5)
  axis(side = 1, at = colSums(mp)/2, labels = dimnames(summs)[[3]], las = 2)
  box()
}
```

```{r vals_plots fn}
vals_plots = function(x, main) {
  par(mfrow = c(1,3), oma = c(0,2,2,0))
  vals_plot(x[,c("obs", "sim"),"cv",], main = "CV")
  vals_plot(x[,c("obs", "sim"),"mean",], main = "Mean")
  vals_plot(x[,c("obs", "sim"),"acf",], main = "ACF")
  mtext(side = 2, outer = TRUE, adj = 0.75, line = 1, "Value")
  mtext(side = 3, outer = TRUE, line = 0.5, main, cex = 1.25, font = 2)
}
```

>>>>

```{r ratio_plot fn}
ratio_plot = function(ratios, line_y, pt_fn = mean, ylim = NULL, ylab = FALSE, ...) {

@@

  # set graphics parameters
  par(mar = c(7,1.25,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")

  # make an empty plot with the right dimensions
  if (is.null(ylim)) {
    ymin = 0
    ymax = max(2, max(summs, na.rm = TRUE) * 1.025)
  } else {
    ymin = ylim[1]
    ymax = ylim[2]
  }

  mp = barplot(summs["50%",], col = "white", xlab = "", border = "white", las = 2,
               ylim = c(ymin, ymax), ylab = "", ...)

  if (ylab) {
    mtext(side = 2, line = 2.25, "Ratio (Sim:Obs)")
  }

@@

  # create an "acceptable region"
  usr = par("usr"); rect(usr[1], line_y - 0.2, usr[2], line_y + 0.2, col = "grey90", border = NA)
  abline(h = line_y, lty = 2, col = "grey")

@@

```{r ratio_plots fn}
ratio_plots = function(x, main) {
  par(mfrow = c(1,3), oma = c(0,2.5,2,0))
  ratio_plot(x[,"sim-v-obs","cv",], main = "CV", pt_fn = geomean, line_y = 1, ylab = TRUE)
  ratio_plot(x[,"sim-v-obs","mean",], main = "Mean", pt_fn = geomean, line_y = 1)
  ratio_plot(x[,"sim-v-obs","acf",], main = "ACF (Sim - Obs)", pt_fn = mean, line_y = 0, ylim = c(-1,1))
  mtext(side = 3, outer = TRUE, line = 0.5, main, cex = 1.25, font = 2)
}
```

```{r vals_plot fn}
vals_plot = function(vals, legend = FALSE, ylab = FALSE, ...) {
  f = function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975), na.rm = TRUE)

@@

  par(mar = c(7,1.25,1,1), mgp = c(2,0.35,0), tcl = -0.15, lend = "square", ljoin = "mitre")
  mp = barplot(summs[,"50%",], beside = TRUE, col = "white", border = "white", ylim = range(summs, na.rm = TRUE) + diff(range(summs, na.rm = TRUE)) * c(-0.05,0.05), xaxt = "n", ...)

  if (ylab) {
    mtext(side = 2, line = 2.25, "Value")
  }

  segments(mp, summs[,"2.5%",], mp, summs[,"97.5%",], col = c("salmon", "royalblue"))
  segments(mp, summs[,"25%",], mp, summs[,"75%",], col = c("salmon", "royalblue"), lwd = 6)
  points(y = summs[,"50%",], x = mp, col = c("salmon", "royalblue"), pch = 3, cex = 1.5)
  axis(side = 1, at = colSums(mp)/2, labels = dimnames(summs)[[3]], las = 2)
  box()

  if (legend) {
    legend("topleft", legend = c("Obs", "Sim"), pch = 15, col = c("salmon", "royalblue"), pt.cex = 1.75, bty = "n")
  }
}
```

```{r vals_plots fn}
vals_plots = function(x, main) {
  par(mfrow = c(1,3), oma = c(0,2.5,2,0))
  vals_plot(x[,c("obs", "sim"),"cv",], main = "CV", legend = TRUE, ylab = TRUE)
  vals_plot(x[,c("obs", "sim"),"mean",], main = "Mean")
  vals_plot(x[,c("obs", "sim"),"acf",], main = "ACF")
  mtext(side = 3, outer = TRUE, line = 0.5, main, cex = 1.25, font = 2)
}
```
